---
title: "Adopting different terminologies"
author: "Mabi Harandi"
date: "6/30/2018"
output: html_document
---

``````{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(rjson)
library(plyr)
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(reshape2)
library(scales)
library(data.table)
library(jtools)
library(sjPlot)
library(sjmisc)




 #df <- read.csv('3terms_first_month.csv')
# 
# 
 #df_nosciteam <- df[which(!df$user %in% c("mcoughlin","srallen-tester","srallen","crowston","mzevin1","trouille","cjackso3","costerlusyr.edu","Mabi", "parrish","citizenscientist1994","camallen","sciencejedi","jessiemcd", "ejm553","RF45","lcalian","joeykey","isapatane","uber_pye","olipatane","areeda","jafeldt","lmp579","Carsten","Sarah Allen","Mike Zevin","matsoulina","Jrsmith02","sbc538","zooniverse","Jack_Larson","emmabublitz","tlafky","SammiHoar","Pritchet","lucycawte","meredithspalmer","shuebner729", "Jamee64","jmuddappa","tillydad","davidbygott","maricksu", "trouille","jessdewey","AniKarenina","haleyxmoon","schn1007","julesolson","ItsKatniss","Keeganlim1205","Danaerys","mouri010","mineaca","aliburchard")),]
# 
# 
# 
# # df_nosciteam_M_G <- df_nosciteam[ which( !(df_nosciteam$Project == "gravityspy" & df_nosciteam$Month < 8)) , ]
# # df_nosciteam_M_G_S <- df_nosciteam_M_G[ which( !(df_nosciteam_M_G$Project == "snapshot" & df_nosciteam_M_G$Month > 17)) , ]
# # 
# # 
# # df_nosciteam_M_G_S$Month[(df_nosciteam_M_G_S$Project == "gravityspy" & df_nosciteam_M_G_S$Month ==8)] <- "1"
# 
  #num_days <- ddply(df_nosciteam, c("Project", "user"), summarize,
             #         Days = length(unique(Date1)))
  #active_users <- num_days[which(num_days$Days >1),]
# # 
  #df_active_users <- df_nosciteam[which(df_nosciteam$user %in% active_users$user),]
  #write.csv(df_active_users,"df_active_users.csv")
# #                     
# # 
#  df_class <- df_active_users[which(df_active_users$term == "class"),]
# df_nonclass <- df_active_users[which(df_active_users$term == "nonclass"),]

# 
#write.csv(df_class, "df_class.csv")
# 
# write.csv(df_nonclass, "df_nonclass.csv")



df_class <- read.csv('df_class.csv')
df_nonclass <- read.csv('df_nonclass.csv')

df_experienced <- read.csv('experienced_users_Month_G_S.csv')
df_E_class <- df_experienced[which(df_experienced$term == "class"),]
df_E_nonclass <- df_experienced[which(df_experienced$term == "nonclass"),]



```



The datat of Gravity Spy is collected from 2016-03-09 to 2018-02-10.
The dataset of Snapshot Serengeti is collected from 2012-12-11 to 2016-02-29.

Linear model for Newcomers and Experienced users over labels and domain terms

#Newcomers-Labels

```{r classterms, echo=FALSE}



df_class2 <- df_class[which(df_class$total >= 1),]
#df_class2 <-df_class2[which(df_class2$Month <=23),]
Normalized_TF_classes <- ddply(df_class2, c("Project", "Month"), summarize,
                     total_terms = sum(total),
                     class_Total = sum(count),
                     Normalized_TF = class_Total/total_terms,
                     Normalized_TF_Mean = mean(count/total),
                     Users = length(unique(user)))



Normalized_TF_classes_summary <- ddply(df_class2, c("Project"), summarize,
                     Users = length(unique(user)),
                     Months = length(unique(Month)),
                     class_Total = sum(count),
	                   class_Mean = mean(count),
	                   class_Median = median(count),
	                   class_SD = sd(count, na.rm = TRUE),
	                   class_Var = var(count),
                     total_terms = sum(total),
                     Normalized_TF = class_Total/total_terms,
                     Normalized_TF_Mean = mean(class_Total/total_terms),
	                   Normalized_TF_Median = median(class_Total/total_terms),
	                   Normalized_TF_SD = sd(class_Total/total_terms, na.rm = TRUE),
	                   Normalized_TF_Var = var(class_Total/total_terms))


Normalized_TF_plot <- ggplot(data=Normalized_TF_classes, aes(x=Month, y=Normalized_TF_Mean, group=Project)) +
  ggtitle("Distribution of class terms Normalized_TF")+
  geom_line( color="blue", size=.5)+
  xlim(1,30) + 
  facet_grid(facets = Project ~ ., scales="free", margins = FALSE) +  
  geom_point(color="red", aes(size=Users)) +
  geom_text(aes(label=Users,hjust=0, vjust=0))


#DTs <- Normalized_TF_classes[which(Normalized_TF_classes$Month <=24),]
summary_interact <- summary(lm(Normalized_TF ~ Month + Project + Month*Project , data = Normalized_TF_classes, na.action = "na.exclude"))
plot_s <- lm(Normalized_TF ~ Month + Project + Month*Project , data = Normalized_TF_classes, na.action = "na.exclude")
 
interactplot <- interact_plot(plot_s, pred = "Month", modx = "Project", main.title ="Normalized_TF of label terms-Newcomers")
# + theme_apa(legend.pos = "right", legend.use.title = FALSE, x.font.size = 16, y.font.size = 16)




```




```{r classterms.info, include=TRUE, echo=FALSE}

Normalized_TF_classes_summary
Normalized_TF_plot
summary_interact
interactplot

```

#Experienced-Labels

```{r Eclassterms, echo=FALSE}



df_E_class2 <- df_E_class[which(df_E_class$total >= 1),]
df_E_class2 <-df_E_class2[which(df_E_class2$Month <=24),]
Normalized_TF_classes <- ddply(df_E_class2, c("Project", "Month"), summarize,
                     total_terms = sum(total),
                     class_Total = sum(count),
                     Normalized_TF = class_Total/total_terms,
                     Normalized_TF_Mean = mean(count/total),
                     Users = length(unique(user)))



Normalized_TF_classes_summary <- ddply(df_E_class2, c("Project"), summarize,
                     Users = length(unique(user)),
                     Months = length(unique(Month)),
                     class_Total = sum(count),
	                   class_Mean = mean(count),
	                   class_Median = median(count),
	                   class_SD = sd(count, na.rm = TRUE),
	                   class_Var = var(count),
                     total_terms = sum(total),
                     Normalized_TF = class_Total/total_terms,
                     Normalized_TF_Mean = mean(class_Total/total_terms),
	                   Normalized_TF_Median = median(class_Total/total_terms),
	                   Normalized_TF_SD = sd(class_Total/total_terms, na.rm = TRUE),
	                   Normalized_TF_Var = var(class_Total/total_terms))


Normalized_TF_plot <- ggplot(data=Normalized_TF_classes, aes(x=Month, y=Normalized_TF_Mean, group=Project)) +
  ggtitle("Distribution of class terms Normalized_TF")+
  geom_line( color="blue", size=.5)+
  xlim(1,30) + 
  facet_grid(facets = Project ~ ., scales="free", margins = FALSE) +  
  geom_point(color="red", aes(size=Users)) +
  geom_text(aes(label=Users,hjust=0, vjust=0))


#DTs <- Normalized_TF_classes[which(Normalized_TF_classes$Month <=24),]
summary_interact <- summary(lm(Normalized_TF ~ Month + Project + Month*Project , data = Normalized_TF_classes, na.action = "na.exclude"))
plot_s <- lm(Normalized_TF ~ Month + Project + Month*Project , data = Normalized_TF_classes, na.action = "na.exclude")
 
interactplot <- interact_plot(plot_s, pred = "Month", modx = "Project", main.title ="Normalized_TF of label terms-Experienced Users")
# + theme_apa(legend.pos = "right", legend.use.title = FALSE, x.font.size = 16, y.font.size = 16)




```

```{r Eclassterms.info, include=TRUE, echo=FALSE}

Normalized_TF_classes_summary
Normalized_TF_plot
summary_interact
interactplot

```

In this plot we see the Normalized_TF of domain(non-class) terms that volunteers have used in the first month that they have strated commenting.

#Newcomers-Domain terms

```{r nonclassterms, echo=FALSE}



df_nonclass2 <- df_nonclass[which(df_nonclass$total >= 1),]
#df_nonclass2 <-df_nonclass2[which(df_nonclass2$Month <=23),]
Normalized_TF_nonclasses <- ddply(df_nonclass2, c("Project","Month"), summarize,
                     total_terms = sum(total),
                     nonclass_Total = sum(count),
                     Normalized_TF = nonclass_Total/total_terms,
                     Normalized_TF_Mean = mean(count/total),
                     Users = length(unique(user))
)
Normalized_TF_nonclasses_summary <- ddply(df_nonclass2, c("Project"), summarize,
                     Users = length(unique(user)),
                     Months = length(unique(Month)),
                     nonclass_Total = sum(count),
	                   nonclass_Mean = mean(count),
	                   nonclass_Median = median(count),
	                   nonclass_SD = sd(count, na.rm = TRUE),
	                   nonclass_Var = var(count),
                     total_terms = sum(total),
                     Normalized_TF = nonclass_Total/total_terms,
                     Normalized_TF_Mean = mean(nonclass_Total/total_terms),
	                   Normalized_TF_Median = median(nonclass_Total/total_terms),
	                   Normalized_TF_SD = sd(nonclass_Total/total_terms, na.rm = TRUE),
	                   Normalized_TF_Var = var(nonclass_Total/total_terms))


Normalized_TF_plot_nonclasses <- ggplot(data=Normalized_TF_nonclasses, aes(x=Month, y=Normalized_TF_Mean, group=Project)) +
  ggtitle("Distribution of non-class terms Normalized_TF")+
  geom_line( color="blue", size=.5)+
  xlim(1,30) + 
  facet_grid(facets = Project ~ ., scales="free", margins = FALSE) +  
  geom_point(color="red" , aes(size=Users))+
  geom_text(aes(label=Users,hjust=0, vjust=0))


#DTs <- Normalized_TF_nonclasses[which(Normalized_TF_nonclasses$Month <=24),]
summary_interact_nonclasses <- summary(lm(Normalized_TF ~ Month + Project + Month*Project , data = Normalized_TF_nonclasses, na.action = "na.exclude"))
plot_ns <- lm(Normalized_TF ~ Month + Project + Month*Project , data = Normalized_TF_nonclasses, na.action = "na.exclude")
interactplot_nonclasses <- interact_plot(plot_ns, pred = "Month", modx = "Project", main.title ="Normalized_TF of popular domain terms-Newcomers") # + theme_apa(legend.pos = "right", legend.use.title = FALSE, x.font.size = 16, y.font.size = 16)

```



```{r nonclassterms.info, include=TRUE, echo=FALSE}

Normalized_TF_nonclasses_summary
Normalized_TF_plot_nonclasses
summary_interact_nonclasses
interactplot_nonclasses
```


#Experienced-Domain terms
```{r Enonclassterms, echo=FALSE}



df_E_nonclass2 <- df_E_nonclass[which(df_E_nonclass$total >= 1),]
df_E_nonclass2 <-df_E_nonclass2[which(df_E_nonclass2$Month <=24),]
Normalized_TF_nonclasses <- ddply(df_E_nonclass2, c("Project","Month"), summarize,
                     total_terms = sum(total),
                     nonclass_Total = sum(count),
                     Normalized_TF = nonclass_Total/total_terms,
                     Normalized_TF_Mean = mean(count/total),
                     Users = length(unique(user))
)
Normalized_TF_nonclasses_summary <- ddply(df_E_nonclass2, c("Project"), summarize,
                     Users = length(unique(user)),
                     Months = length(unique(Month)),
                     nonclass_Total = sum(count),
	                   nonclass_Mean = mean(count),
	                   nonclass_Median = median(count),
	                   nonclass_SD = sd(count, na.rm = TRUE),
	                   nonclass_Var = var(count),
                     total_terms = sum(total),
                     Normalized_TF = nonclass_Total/total_terms,
                     Normalized_TF_Mean = mean(nonclass_Total/total_terms),
	                   Normalized_TF_Median = median(nonclass_Total/total_terms),
	                   Normalized_TF_SD = sd(nonclass_Total/total_terms, na.rm = TRUE),
	                   Normalized_TF_Var = var(nonclass_Total/total_terms))


Normalized_TF_plot_nonclasses <- ggplot(data=Normalized_TF_nonclasses, aes(x=Month, y=Normalized_TF_Mean, group=Project)) +
  ggtitle("Distribution of non-class terms Normalized_TF")+
  geom_line( color="blue", size=.5)+
  xlim(1,30) + 
  facet_grid(facets = Project ~ ., scales="free", margins = FALSE) +  
  geom_point(color="red" , aes(size=Users))+
  geom_text(aes(label=Users,hjust=0, vjust=0))


#DTs <- Normalized_TF_nonclasses[which(Normalized_TF_nonclasses$Month <=24),]
summary_interact_nonclasses <- summary(lm(Normalized_TF ~ Month + Project + Month*Project , data = Normalized_TF_nonclasses, na.action = "na.exclude"))
plot_ns <- lm(Normalized_TF ~ Month + Project + Month*Project , data = Normalized_TF_nonclasses, na.action = "na.exclude")
interactplot_nonclasses <- interact_plot(plot_ns, pred = "Month", modx = "Project", main.title ="Normalized_TF of popular domain terms-Experienced") # + theme_apa(legend.pos = "right", legend.use.title = FALSE, x.font.size = 16, y.font.size = 16)

```



```{r Enonclassterms.info, include=TRUE, echo=FALSE}

Normalized_TF_nonclasses_summary
Normalized_TF_plot_nonclasses
summary_interact_nonclasses
interactplot_nonclasses
```





